%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{ #1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{https://github.com/jacobbroderick}{\Large Jacob Broderick}} & Email : \href{mailto:jacobabroderick@gmail.com}{jacobabroderick@gmail.com}\\
		& Mobile : 541-973-3736 \\
	\end{tabular*}
	
		%--------PROGRAMMING SKILLS------------
	\section{Technical Expertise}
	\resumeSubHeadingListStart
	\resumeSubItem
	{Languages}{: C\#, SQL, Python, HTML/CSS, Javascript/Jquery}
	\resumeSubItem{Technologies}{.Net MVC, Git, SVN, Microsoft SQL Server 2008, Agile, TFS}
	
	\resumeSubHeadingListEnd

	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
		\resumeSubheading
	{OfficeAlly}{Vancouver, WA}
	{Database Developer}{Jan 2018 - Present}
	\resumeItemListStart
	\resumeItem
	{Transitioned databases to SVN to ensure that changes are properly tracked}
	\resumeItem
	{Created a Jenkins workflow that allows for changes to databases to automatically be built on the development server, allowing for continuous integration between development and test environments.}
	\resumeItem{Designed tables and stored procedures based on the needs of new features that met the performance needs of the system}
	\resumeItem{Refactored old tables and stored procedures to improve their performance and usability causing a reduction in time for the database to return data}
	\resumeItem{Influenced design decisions with a focus on data to ensure that the back end code utilizes the database which lead to a faster and easier to work with design}
	\resumeItemListEnd
	
	\resumeSubheading
	{Coelo, Company by Design}{Corvallis, OR}
	{Software Engineer}{Jun 2017 - Nov 2017}
	\resumeItemListStart
	\resumeItem
	{Processed images of fish in C\# resulting in data being saved for lab technicians saving many hours per week.
	}
	\resumeItem
	{Designed and implemented prototypes with the purpose of updating deprecated machine learning software to perform updated requirements.}
	\resumeItemListEnd
	
	\resumeSubheading
	{HP inc.}{Corvallis, OR}
	{Software Engineering Intern}{Jun 2016 - Aug 2016}
	\resumeItemListStart
	\resumeItem{Created an Oracle SQL database object that saves time by computing over 40 terrabytes of data ahead of time.}
	\resumeItem{Queried a big data database for information regarding ink using SQL which resulted in managers finding errors in processes more quickly.}
	\resumeItemListEnd
	
	\resumeSubheading{Center for Applied Systems and Software}{Corvallis, OR}{Student Software Developer}{May 2014 - Jun 2015, Sep 2015 - Jun 2016}
	\resumeItemListStart
	\resumeItem{Member of Agile team responsible for the design and implementation of a restful interface for an ODOT emergency response application which reduced the response time of emergency teams in the state of Oregon.}
	\resumeItem{All projects were documented using specific government document formats and stored in Microsoft team foundation services.}
	\resumeItem{Created an interface to the travel time system seen on Oregon highways that allows outside counties to make use of the system and stored information for ODOT to predict traffic trends.}
	%\resumeItem{Mobile Web App, JQuery, Jasmine}{Created a prototype and Jasmine test suite for a fish market app using Sencha Touch and Phone Gap for Oregon SeaGrant allowing users to find which fish are being sold on the Oregon Coast.}
	\resumeItemListEnd
	
	%\resumeSubheading{Center for Applied Systems and Software}{Corvallis, OR}{Student Test Engineer}{Jun 2015 - Sep 2015}
	%\resumeItemListStart
	%\resumeItem{Python}{Created automated tests with TCL and Python which saved active time during tests that could take 3 or more hours.}
	%\resumeItemListEnd
	
	
	
	
	\resumeSubHeadingListEnd

		%-----------PROJECTS-----------------
		%\section{Projects}
		%\resumeSubHeadingListStart
		%\resumeSubItem{Simple Raft Implementation}{Simple implementation of the raft consensus algorithm in Go. The raft algorithm prevents data loss by having a leader copy it's data to child processes. In the case of %an error the algorithm will elect a new leader and all other servers will keep up to date with the new leader. Developed leadership voting and server connection algorithms, and learned about distributed systems %algorithms.}
		%\resumeSubItem{Starcraft AI}{Worked on a senior project team with well documented requirements. Created a working AI that would play the game Starcraft Brood War using an API designed for controlling the game. %The project was required to be well documented and clean to allow other students to continue the project. Built with C++ using Visual Studio with git as version control.}
	%	\resumeSubHeadingListEnd
	

	%


	%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Oregon State University}{Corvallis, OR}
{Bachelor of Science in Computer Science with applied option in Security}{2017}
\resumeSubHeadingListEnd

	
	%-------------------------------------------
\end{document}
